% this file is called up by thesis.tex
% content in this file will be fed into the main document

\chapter{Aims of the project} % top level followed by section, subsection


% ----------------------- contents from here ------------------------

\section{Final Aim}

The Ultimate goal of the project is to developed a distributed system for use in an automotive environment. This will culminate into a completed system, provided data logging functionality and a user interface to view the live data.

\section{Goals}

The goals this project aimed to achieve were set out as follows.

\begin{enumerate}
\item  Investigate the use messaging protocols inside a minimal embedded systems
\item  Develop GPS capability
\item  Develop Battery monitor capabilty
\item  Integrate this data into a user display
\item  Log this data to be reviewed later
\end{enumerate}

During development, the author also kept the following goals in-line, to make the system easier to develop for.  This was done to give the software a better chance of being developed further by future projects on this topic.


\begin{enumerate}
\item  Allow the system to be easily extend-able
\item  Attempt to minimize future exposure to concurrency
\item  Use simpler individual designs, to make it easier for engineers (as opposed to programmers) to modify
\item Develop standards for inter-module communication
\item Develop common UI elements to facilitate ease-of-layout and interface design.
\item Develop the system in such a way that it is portable to other devices. The hardware used is slightly older, and the system will be developed in a way that it can be ported across to new hardware.
\end{enumerate}


% ---------------------------------------------------------------------------
% ----------------------- end of thesis sub-document ------------------------
% ---------------------------------------------------------------------------